Results

### 2018-03-19 results-simus-pres.Rmd
figures for pres

---
title: "Results"
author: "Florian Privé"
date: "November 17, 2017"
output: 
  html_document:
    code_folding: hide
---

@@

format_results <- function(results) {
  results %>%
    as_tibble() %>%
    mutate(
      par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                          levels = c("30 in HLA", paste(3 * 10^(1:3), "in all"))),
      AUC = map_dbl(eval, ~ bigstatsr::AUC(.x[, 1], .x[, 2])),
      pAUC = map_dbl(eval, ~ pAUC(.x[, 1], .x[, 2]))
    )
}
```

@@

barplot_causal_one <- function(results, h2) {

  auc_max <- `if`(h2 == 0.8, 0.94, 0.84)

  results %>%
    filter(par.h2 == h2) %>%
    barplot_causal() +
    geom_hline(yintercept = auc_max, linetype = 3, color = "blue") +
    facet_grid(par.dist ~ .)
}

barplot_causal_all <- function(results) {

  results %>%
    barplot_causal() +
    geom_hline(aes(yintercept = auc_max), linetype = 3, color = "blue",
               data = data.frame(par.h2 = c(0.5, 0.8), auc_max = c(0.84, 0.94))) +
    facet_grid(par.dist ~ par.h2)
}
```

@@

  results <- filter(
    results, method %in% c("logit-simple", with_method), par.h2 == 0.8)

  results.summary <- results %>%
    group_by_at(c(vars(starts_with("par")), "method")) %>%
    summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
    print(n = Inf)

@@

    results %>%
      myggplot() +
      geom_boxplot(aes_string("par.causal", y, color = "method", 
                              fill = "method"), alpha = 0.3) + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      facet_grid(par.model ~ par.dist) +
      labs(x = "Causal SNPs (number and location)", y = ylab, 
           fill = "Method", color = "Method") +
      theme(legend.position = "none") +
      scale_fill_manual(values = methods.color) +
      scale_color_manual(values = methods.color) +
      scale_y_continuous(limits = c(0, NA))
  }

  p1 <- results.summary %>%
    barplot_causal_one(h2 = 0.8) +
    facet_grid(par.model ~ par.dist) +
    labs(y = sprintf("Mean of %d AUCs", nsimu))

  p2 <- cowplot::plot_grid(
    plot_extra("nb.preds", "Number of predictors"),
    plot_extra("timing", "Execution time (in seconds)"),
    ncol = 1, align = "hv", scale = 0.95, 
    labels = LETTERS[2:3], label_size = 20
  )

@@

ggsave("figures/supp-ttrees.pdf", scale = 1/100, width = 1400, height = 1060)
```

@@

results2.summary <- results2 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  print(n = Inf) 
```

@@

ggsave("figures/supp-triple.pdf", scale = 1/100, width = 1400, height = 1060)
```

```{r}
results2.summary %>%
  filter(grepl("logit", method)) %>%
  barplot_causal_one(h2 = 0.5) +
  facet_grid(par.model ~ par.dist)

ggsave("figures/supp-AUC-triple.pdf", scale = 1/110, width = 1242, height = 951)
```

### Results with model fancy

```{r}
results2.summary %>%
  filter(par.model == "fancy", method %in% c("logit-simple", "PRS-max")) %>%
  barplot_causal_all()

ggsave("figures/supp-AUC-logit-fancy.pdf", scale = 1/110, width = 1242, height = 951)
```

```{r}
results2.summary %>%
  filter(par.model == "fancy", grepl("PRS", method)) %>%
  barplot_causal_all()

ggsave("figures/supp-AUC-PRS-fancy.pdf", scale = 1/110, width = 1242, height = 951)
```

@@

### Correlation between predictive measures

@@

```{r, fig.asp=0.7, out.width="95%", fig.width=16}
results3 %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  mutate(Parameters  = interaction(par.h2, par.dist, method, sep = " | ")) %>%
  myggplot(aes(AUC, pAUC, color = Parameters)) + 
  geom_point(size = 0.6, alpha = 0.5) +
  geom_smooth(aes(linetype = Parameters), method = "loess", se = FALSE, size = 2) +
  theme(legend.key.width = unit(3.5, "line"), 
        legend.direction = "horizontal") + 
  labs(y = "Partial AUC (specificity: [0.9, 1])") +
  theme(legend.position = "top", axis.title = element_text(size = rel(2.2))) +

ggsave("figures/supp-AUC-corr.pdf", scale = 1/100, width = 1525, height = 983)
```

```{r}
cor(results3$AUC, results3$pAUC, method = "spearman")
```

@@

```{r}
results3.summary <- results3 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  print(n = Inf)
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(method %in% c("logit-simple", "PRS-max"), par.model == "simple") %>%
  barplot_causal_one(h2 = 0.8)

ggsave("figures/main-AUC-logit.pdf", scale = 1/90, width = 844, height = 872)
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(grepl("PRS", method)) %>%
  barplot_causal_one(h2 = 0.8)

ggsave("figures/main-AUC-PRS.pdf", scale = 1/90, width = 844, height = 872)
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  barplot_causal_one(h2 = 0.5)

ggsave("figures/supp-AUC-logit.pdf", scale = 1/90, width = 844, height = 872)
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(grepl("PRS", method)) %>%
  barplot_causal_one(h2 = 0.5)

ggsave("figures/supp-AUC-PRS.pdf", scale = 1/90, width = 844, height = 872)
```

@@

results4 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  print(n = Inf)

@@

```{r, fig.asp = 1, out.width = "90%"}
results34 %>%
  myggplot() +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = auc_max), linetype = 3, color = "blue",
             data = data.frame(par.h2 = c(0.5, 0.8), auc_max = c(0.84, 0.94))) +
  geom_boxplot(aes(method, AUC, fill = simu, color = simu), alpha = 0.3) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(par.model ~ par.causal) +
  facet_grid(par.h2 + par.dist ~ par.causal) +
  scale_fill_brewer(type = "qual", palette = 2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  labs(x = "Method")

ggsave("figures/supp-AUC-chr6.pdf", scale = 1/110, width = 1153, height = 908)
```

@@

results5.summary <- results5 %>%
  group_by_at(c(vars(starts_with("par")), "method", "n.train")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  print(n = Inf)

@@

```{r}
myggplot(results35.summary, aes(n.train, AUC_mean, color = method, linetype = method)) +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = auc_max), linetype = 3, color = "blue",
             data = data.frame(par.h2 = c(0.5, 0.8), auc_max = c(0.84, 0.94))) +
  geom_line(size = 1.5) +
  geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, 
                    ymax = AUC_mean + 2 * AUC_boot), 
                size = 1.5, width = 0) +
  facet_grid(par.h2 ~ par.dist) +
  scale_x_continuous(breaks = 1:6 * 1000, minor_breaks = NULL) + 
  scale_y_continuous(minor_breaks = 0:20 / 20) +
  scale_color_manual(values = methods.color) +
  labs(x = "Size of the training set", y = "Mean of 100 AUCs", 
       color = "Method", linetype = "Method") +
  theme(legend.key.width = unit(3, "line"))

ggsave("figures/main-AUC-ntrain.pdf", scale = 1/100, width = 1050, height = 800)
```

>>>>

---
title: "Results"
author: "Florian Privé"
date: "March 19, 2018"
output: 
  html_document:
    code_folding: hide
---

@@

format_results <- function(results) {
  results %>%
    as_tibble() %>%
    filter(par.h2 == 0.8, par.dist == "gaussian") %>%
    mutate(
      par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                          levels = c("30 in HLA", paste(3 * 10^(1:3), "in all"))),
      AUC = map_dbl(eval, ~ bigstatsr::AUC(.x[, 1], .x[, 2])),
      pAUC = map_dbl(eval, ~ pAUC(.x[, 1], .x[, 2]))
    )
}
```

@@

barplot_causal_one <- function(results) {

  results %>%
    barplot_causal() +
    geom_hline(yintercept = 0.94, linetype = 3, color = "blue") +
    facet_grid(par.dist ~ .)
}
```

@@

  results <- filter(results, method %in% c("logit-simple", with_method))

  results.summary <- results %>%
    group_by_at(c(vars(starts_with("par")), "method")) %>%
    summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())

@@

    results %>%
      myggplot() +
      geom_boxplot(aes_string("par.causal", y, color = "method", 
                              fill = "method"), alpha = 0.3) + 
      theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
      # facet_grid(par.model ~ par.dist) +
      labs(x = "Causal SNPs (number and location)", y = ylab, 
           fill = "Method", color = "Method") +
      theme(legend.position = "none") +
      scale_fill_manual(values = methods.color) +
      scale_color_manual(values = methods.color) +
      scale_y_continuous(limits = c(0, NA))
  }

  p1 <- results.summary %>%
    barplot_causal_one() +
    facet_grid(par.model ~ par.dist) +
    labs(y = sprintf("Mean of %d AUCs", nsimu))

  p2 <- cowplot::plot_grid(
    plot_extra("nb.preds", "Number of predictors"),
    plot_extra("timing", "Execution time (in seconds)"),
    ncol = 1, align = "hv", scale = 0.90, 
    labels = LETTERS[2:3], label_size = 20
  )

@@

ggsave("figures/pres-ttrees.svg", scale = 1/100, width = 1300, height = 1060)
```

@@

results2.summary <- results2 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())
```

@@

ggsave("figures/pres-triple.svg", scale = 1/100, width = 1300, height = 1060)
```

@@

@@

@@

```{r}
results3.summary <- results3 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  barplot_causal_one()

ggsave("figures/pres-AUC-logit.svg", scale = 1/110, width = 1045, height = 770)
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(grepl("PRS", method)) %>%
  barplot_causal_one()

ggsave("figures/pres-AUC-PRS.svg", scale = 1/110, width = 1045, height = 770)
```

@@

results4 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())

@@

```{r, fig.asp = 1, out.width = "90%"}
results34 %>%
  filter(par.h2 == 0.8, par.dist == "gaussian", method %in% c("logit-simple", "PRS-max")) %>%
  myggplot() +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = 0.94), linetype = 3, color = "blue") +
  geom_boxplot(aes(method, AUC, fill = simu, color = simu), alpha = 0.3) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_grid(par.dist ~ par.causal) +
  scale_fill_brewer(type = "qual", palette = 2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  labs(x = "Method")

ggsave("figures/pres-AUC-chr6.svg", scale = 1/110, width = 990, height = 700)
```

@@

results5.summary <- results5 %>%
  group_by_at(c(vars(starts_with("par")), "method", "n.train")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())

@@

```{r}
results35.summary %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  myggplot(aes(n.train, AUC_mean, color = method, linetype = method)) +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = 0.94), linetype = 3, color = "blue") +
  geom_line(size = 1.5) +
  geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, 
                    ymax = AUC_mean + 2 * AUC_boot), 
                size = 1.5, width = 0) +
  facet_grid(. ~ par.dist) +
  scale_x_continuous(breaks = 1:6 * 1000, minor_breaks = NULL) + 
  scale_y_continuous(minor_breaks = 0:20 / 20) +
  scale_color_manual(values = methods.color) +
  labs(x = "Size of the training set", y = "Mean of 100 AUCs", 
       color = "Method", linetype = "Method") +
  theme(legend.key.width = unit(3, "line"))

ggsave("figures/pres-AUC-ntrain.svg", scale = 1/100, width = 870, height = 635)
```
